---
title: "Individual Machine Learning Capstone"
author: "Russell Matthew Bayes"
date: "07/12/2021"
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Overview 
This project is the second assignment of the 'Data Science: Capstone' course (PH125.9x), offered by edX HarvardX. The aim of this project is to use a publicly available dataset to apply machine learning techniques that go beyond standard linear regression and to clearly communicate the process and insights gained from the analysis.

## Introduction
This is a multivariate type of dataset which means providing or involving a variety of separate mathematical or statistical variables, multivariate numerical data analysis. It is composed of 14 attributes which are age, sex, chest pain type, resting blood pressure, serum cholesterol, fasting blood sugar, resting electrocardiographic results, maximum heart rate achieved, exercise-induced angina, oldpeak — ST depression induced by exercise relative to rest, the slope of the peak exercise ST segment, number of major vessels and Thalassemia. This database includes 76 attributes, but all published studies relate to the use of a subset of 14 of them. The Cleveland database is the only one used by ML researchers to date. One of the major tasks on this dataset 

##
Traffic volume on a road is defined as the number of vehicles passing the measurement point per unit time. The traffic counts can be used by local councils to identify which routes are used most and to either improve that road or provide an alternative if there is an excessive amount of traffic [[1](https://en.wikipedia.org/wiki/Traffic_count)]. 


## Project Description
The objective of this project is to use machine learning models to predict the occurrences of heart  and understand what features are important to explain the occurrences of heart. Data imputation usug a number of methods are included to improve the predictions and, as various modeling approaches are presented, the best model will be selected based on metrics such as the RMSE.

## Dataset

The present project studies the Metro Interstate Traffic Volume Dataset, available at the [kaggle.com](https://www.kaggle.com/redwankarimsony/heart-disease-data) [[1](https://www.kaggle.com/redwankarimsony/heart-disease-data)]. The main purpose of this dataset is to predict Heart Disease based on the given attributes of a individual that whether that particular person has heart disease or not.

It is composed of 14 attributes which are age, sex, chest pain type, resting blood pressure, serum cholesterol, fasting blood sugar, resting electrocardiographic results, maximum heart rate achieved, exercise-induced angina, oldpeak — ST depression induced by exercise relative to rest, the slope of the peak exercise ST segment, number of major vessels and Thalassemia. This database includes 76 attributes, but all published studies relate to the use of a subset of 14 of them.


The dataset is downloaded directly from the Kaggle.com. 

Data exploration and visualization, as well as transformation and feature engineering, will be presented in the next section.

# Methods and Analysis

## Data Engineering

Before further analysis we need to engineer the data to the desired format, cleaning imputation problems, handling duplications, changing some data type to factor and creating new features.

```{r Importing the data, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
temp <- tempfile()
download.file("https://www.kaggle.com/kaggle/input/heart-disease-data/heart_disease_uci.csv", temp, mode = "wb")
try(gunzip(temp, "heart_disease_uci.csv"))
UCI <- read.csv(temp)
UCI <- read_csv(temp, quote = "\"", col_select = data_cols, na = c(""), show_col_types = FALSE,lazy = FALSE)
rm(temp)
```

The dataset contains `r dim(UCI)[1]` 

```{r message=FALSE, warning=FALSE, echo=FALSE}
glimpse(UCI)
```

T